Toggle Smell Detection in Google Chrome

### 2015-12-08 paper/paper.tex
Add rest of the result section

@@

\section{Conclusion}
\label{conclusion}
TODO

>>>>

\subsection{Average Running time}
The program takes on an average 6 minutes to scan a project containing about 700 to 1000 source files. The scan time is proportional to the number of source files as well as the number of expressions and statements in each file.

@@

\section{Conclusion}
\label{conclusion}
The implementation of the toggle smell detector is practically usable for project using feature toggles. The time taken by the detector is proportional to the size of the project and the smells detected indeed indicate the common problems with the object oriented software like high coupling, low cohesion. Our approach will save lot of time for developers and designers to identify the toggle code smells in source code project, compared to the other approaches like searching through native OS commands or using IDE provided search by reference techniques, which may not accurately indicate a particular smell like spread toggle as it requires examining each toggle flag at various locations.
